Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-18 WSSSPE1_report/WSSSPE1_summary_report.tex
Section 9: Adding a few best practices and issues from Section 3.

@@

\subsubsection*{Workshop process}

The WSSSPE workshop can be viewed as an experiment in how we can
collaboratively and inclusively build a workshop agenda, without asking
large numbers of people to submit papers that will be rejected so that the
workshop can have a low acceptance rate.

@@

Additional activities that are being planned include
two additional WSSSPE workshops at the 2014 SciPy and SC14 conferences.
The SciPy workshop (WSSSPE1.1) will focus on how some software projects
from the SciPy community have dealt with software sustainability issues, both
successfully and unsuccessfully, while the SC14 workshop (WSSSPE2) will
be more general, and will likely focus on determining and publicizing specific
activities that the overall scientific software community can take to move forward.
In addition, there will be a minisymposium on ``Reliable Computational Science''
at the 2014 Society for Industrial and Applied Mathematics (SIAM)
Annual Meeting (SIAM AN14, http://meetings.siam.org)
to further explore some of the key issues raised in
WSSSPE .

>>>>

\subsubsection*{Developing and Supporting Software}

\subsubsection*{Policy}

\subsubsection*{Communities, Models, and Education}

Recognition of scholarship in scientific software over research 
articles is overdue.

@@

\subsubsection*{Developing and Supporting Software}

Successful collaborative projects conducted via the use of shared
repositories ensures reproducibility in computational science.

\subsubsection*{Policy}

\subsubsection*{Communities, Models, and Education}
A sustainability model for scientific software is to build a pipeline
from construction to consumption as found in the most efficient
information technology enterprises.

\subsubsection*{Workshop process}
The WSSSPE workshop can be viewed as an experiment in how we can
collaboratively and inclusively build a workshop agenda, without asking
large numbers of people to submit papers that will be rejected so that the
workshop can have a low acceptance rate.

@@

Additional activities that are being planned include
two additional WSSSPE workshops at the 2014 SciPy and SC14 conferences.
The SciPy workshop (WSSSPE1.1) will focus on how some software projects
from the SciPy community have dealt with software sustainability issues, both
successfully and unsuccessfully, while the SC14 workshop (WSSSPE2) will
be more general, and will likely focus on determining and publicizing specific
activities that the overall scientific software community can take to move forward.
In addition, there will be a minisymposium on ``Reliable Computational Science''
at the 2014 Society for Industrial and Applied Mathematics (SIAM)
Annual Meeting (SIAM AN14, \url{http://meetings.siam.org})
to further explore some of the key issues raised in
WSSSPE.
